A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-11-11 05_calibration_data.Rmd
make model plot square

```{r echo=FALSE}
# patch with residence points and all patches
fig_basic_residence <-
  ggplot()+
  geom_sf(data = griend)+
  geom_point(data = data_res_summary, 
             aes(x_median, y_median),
             size = 10, shape = 7,
             # stroke = ,
             col = "grey20",
             alpha = 1)+
    # geom_path(data = data_recurse,
    #          aes(x, y),
    #         col = "grey", lwd = 0.2)+
  # geom_text(data = data_res_summary,
  #           aes(x_median, y_median,
  #               label = tID),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = 100,
  #           fontface = "bold",
  #           col = "grey20",
  #           alpha = 1)+
  # geom_text(data = patch_summary_data, 
  #           aes(x_median, y_median,
  #               label = patch),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = -50,
  #           fontface = "bold",
  #           col = pal[4],
  #           alpha = 1)+
  geom_point(data = data_recurse,
            aes(x, y,
                col = res_time > 5,
                shape = res_time > 5),
            show.legend = F,
            size = 2)+
  geom_sf(data = patch_sf_data,
          fill = pal[4],
          col = pal[4],
          alpha = 0.3)+
  # geom_segment(data = patch_summary_data,
  #           aes(x = x_end, y = y_end,
  #               xend = shift(x_start, type = "lag"),
  #               yend = shift(y_start, type = "lag")),
  #           col = pal[4], lty = 1,
  #           lwd = 0.5)+
  # geom_point(data = patch_summary_data,
  #            aes(x_median, y_median),
  #            size = 5,
  #            stroke = 1,
  #            col = pal[4],
  #            shape = 1,
  #            show.legend = F)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_shape_manual(values = c(1, 19))+
  scale_fill_distiller(palette = "RdPu")+
  ggspatial::annotation_scale(location = "tl")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631,
           expand = F,
           ylim = c(5901700, 5903150),
           xlim = c(649300, 650700))
```

@@

# add real duration
patch_summary_real[, duration_real := unlist(wp_data)]
# round median coordinate for inferred patches
patch_summary_inferred <- 
  patch_summary_data[, 
                     c("x_median", "y_median", 
                       "nfixes", "duration", "patch")
                     ][, `:=`(x_median = round(x_median, digits = -2),
                              y_median = round(y_median, digits = -2))]

@@

```{r echo=FALSE}
# make figure comparing different methods
figure_patch_duration <-
  ggplot()+
  geom_point(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             show.legend = F,
            size = 3,
            stroke = 2,
            shape = 1,
            col = pal[2])+
  geom_smooth(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             se = F,
             col = pal[1],
             lwd = 1,
             method = "lm",
             show.legend = F)+
  annotate(geom = "text",
           x = 600, y = 1020,
           size = 5,
           label = "R^2 == 0.98",
           parse = T)+
  scale_x_continuous(
    breaks = c(400, 600, 800, 1000),
    labels = as.integer(c(400, 600, 800, 1000) / 60)
    )+
  scale_y_continuous(
    breaks = c(400, 600, 800, 1000),
    labels = as.integer(c(400, 600, 800, 1000) / 60)
  )+
  coord_cartesian(expand = T,
  #             # xlim = c(400, 1050),
  #             ylim = c(250, 1050)
  )+
  geom_abline(slope = 1, lty = 2,
              col = "black")+
  ggthemes::theme_few()+
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.minor = element_line(colour = "grey"))+
  labs(x = "inferred duration (min)",
       y = "real duration (min)")
```

@@

```{r echo=FALSE}
# wrap together
figure_res_patch <-
wrap_plots(list(fig_basic_residence, figure_patch_duration),
           ncol = 1,
           design = "AA\nAA\nAA\nAA\nBB")+
  plot_annotation(tag_levels = "a",
                tag_prefix = "(",
                tag_suffix = ")") &
theme(plot.tag = element_text(face = "bold"))

# save figure
ggsave(figure_res_patch,
       filename = "figures/fig_calib_residence_patch.png",
       height = 225, width = 170, units = "mm")
```

>>>>

```{r echo=FALSE}
# patch with residence points and all patches
fig_basic_residence <-
  ggplot()+
  geom_sf(data = griend)+
  geom_point(data = data_res_summary, 
             aes(x_median, y_median),
             size = 10, shape = 7,
             col = "grey20",
             alpha = 1)+
  geom_point(data = data_recurse,
            aes(x, y,
                col = res_time > 5,
                shape = res_time > 5),
            show.legend = F,
            size = 2)+
  geom_sf(data = patch_sf_data,
          fill = pal[4],
          col = pal[4],
          alpha = 0.3)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_shape_manual(values = c(1, 19))+
  scale_fill_distiller(palette = "RdPu")+
  ggspatial::annotation_scale(location = "tl")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631,
           expand = F,
           ylim = c(5901700, 5903150),
           xlim = c(649300, 650700))
```

@@

# add real duration
patch_summary_real[, duration_real := unlist(wp_data)]

# round median coordinate for inferred patches
patch_summary_inferred <- 
  patch_summary_data[, 
                     c("x_median", "y_median", 
                       "nfixes", "duration", "patch")
                     ][, `:=`(x_median = round(x_median, digits = -2),
                              y_median = round(y_median, digits = -2))]

@@

```{r echo=FALSE}
# make figure comparing different methods
figure_patch_duration <-
  ggplot()+
  geom_point(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             show.legend = F,
            size = 2, col = "grey")+
  geom_smooth(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             se = F,
             col = "grey20",
             lwd = 1,
             method = "lm",
             show.legend = F)+
  annotate(geom = "text",
           x = 600, y = 1020,
           size = 5,
           label = "R^2 == 0.98",
           parse = T)+
  scale_x_continuous(
    breaks = 60 * seq(3, 18, 2),
    labels = seq(3, 18, 2)
    )+
  scale_y_continuous(
    breaks = 60 * seq(5, 20, 2),
    labels = seq(5, 20, 2)
  )+
  coord_cartesian(expand = T,
  #             # xlim = c(400, 1050),
  #             ylim = c(250, 1050)
  )+
  geom_abline(slope = 1, lty = 2,
              col = "black")+
  ggthemes::theme_few()+
  labs(x = "inferred duration (min)",
       y = "real duration (min)")
```

@@

```{r echo=FALSE}
# wrap together
figure_res_patch <-
  wrap_plots(list(fig_basic_residence, figure_patch_duration),
             design = "AA\nAA\nB#")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))

# save figure
ggsave(figure_res_patch,
       filename = "figures/fig_calib_residence_patch.png",
       height = 225, width = 150, units = "mm")
```
